Spin canonical rings of log stacky curves

### 2015-11-28 curves-write-up/AIF/changes-summary.tex
added gorensteinness remark in background

\maketitle

Here are the changes we have made in response to the referee's suggestions.

\begin{enumerate}
	\item Paragraph/remark on Gorenstein-ness in ``Introduction''
		section
	\item Use Hilbert polynomial in Example $\_\_\_$
	\item Replace ``best lower approximation'' with Hirzebruch--Jung
		fractions
	\item (Not to-do yet) Change notation from $\frac{e_i - 1}{2 e_i}$
		to $\frac{e'_i}{2 e'_i + 1}$ where $e'_i = \frac{e_i - 1}{2}$ and
		we range over all $e'_i$ instead of odd $e_i$.
\end{enumerate}

>>>>

\maketitle
\section{Changes Made}
Here are the changes we have made in response to the referee's suggestions.

\begin{enumerate}
	\item We added a remark on Gorensteinness of the log canonical ring following
	the definition of a log spin canonical ring in the background section.
	\item Use Hilbert polynomial in Example $\_\_\_$
	\item Replace ``best lower approximation'' with Hirzebruch--Jung
		fractions
	\item (Not to-do yet) Change notation from $\frac{e_i - 1}{2 e_i}$
		to $\frac{e'_i}{2 e'_i + 1}$ where $e'_i = \frac{e_i - 1}{2}$ and
		we range over all $e'_i$ instead of odd $e_i$.
\end{enumerate}

### 2015-11-28 curves-write-up/spin-cring.tex
added gorensteinness remark in background

>>>>

\begin{rem}
	The log canonical ring, defined to be the direct sum of the even graded pieces of the log spin canonical ring,
	is Gorenstein. It is Cohen Macaulay from \cite[Example 2.5(a)]{watanabe:some-remarks-concerning-demazure's-construction-of-normal-graded-rings}
	and then Gorenstein by \cite[Corollary 2.9]{watanabe:some-remarks-concerning-demazure's-construction-of-normal-graded-rings}.
	In particular, this tells us a log spin canonical curve, the projectivization of a log spin canonical ring,
	is projectively Gorenstein.
\end{rem}
